\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2014-02-21 doc/paper.tex
adding the CPU type to the table head
remove lattice and EFT sections
extend RGE section

\subsection{Model parameters and RGEs}
Even in the simplest supersymmetric model the RGEs form a very large
set of coupled non-linear differential equations.  In a general
(softly broken) supersymmetric theory the soft-breaking parameters
depend on themselves and the susy parameters.  However, the susy
parameters are independent of the soft-breaking parameters [cite: MV,
Staub, Sperling].  This makes it possible to split the model
parameters and their into the following two subsets:
%
\begin{enumerate}
\item \emph{susy parameters:} gauge couplings, superpotential
  parameters and VEVs and
\item soft-breaking parameters.
\end{enumerate}
%
The susy parameters together with their two-loop renormalisation group
equations for the are stored in the class
\code{<model>_susy_parameters}.  The soft-breaking model parameters
together with their two-loop renormalisation group equations for the
are stored in the class \code{<model>_soft_parameters}.  The
dependence of the soft-breaking parameters on the susy parameters is
implemented via inheritance, see
\figurename~\ref{fig:parameter-classes}.
%
\begin{figure}
  \centering
  \tikzumlset{fill class=white}
  \begin{tikzpicture}
    \umlclass[x=0, y=3]{model\_susy\_parameters}{
      - susy parameters
    }{
      + beta()
    }
    \umlclass[x=0, y=0]{model\_soft\_parameters}{
      - soft-breaking parameters
    }{
      + beta()
    }
    \umlinherit{model\_soft\_parameters}{model\_susy\_parameters}
  \end{tikzpicture}
  \caption{Model parameter class structure.}
  \label{fig:parameter-classes}
\end{figure}

@@

\subsection{Lattice method}
If ready.
\subsection{multiple effective models at different scales}
\section{Implementing new models}
\section{Adapting the code at the C++ level}
\section{Using individual modules in your own code}

@@

                          & Intel Core2 Duo            & Intel Core2 Duo             & Intel Xeon\\

@@

\begin{thebibliography}{100}
%\cite{Allanach:2001kg}
\bibitem{Allanach:2001kg} 
  B.~C.~Allanach,
  %``SOFTSUSY: a program for calculating supersymmetric spectra,''
  Comput.\ Phys.\ Commun.\  {\bf 143}, 305 (2002)
  [hep-ph/0104145].
  %%CITATION = HEP-PH/0104145;%%
  %716 citations counted in INSPIRE as of 20 Sep 2013
%\cite{Porod:2003um}
\bibitem{Porod:2003um} 
  W.~Porod,
  %``SPheno, a program for calculating supersymmetric spectra, SUSY particle decays and SUSY particle production at e+ e- colliders,''
  Comput.\ Phys.\ Commun.\  {\bf 153}, 275 (2003)
  [hep-ph/0301101].
  %%CITATION = HEP-PH/0301101;%%
  %413 citations counted in INSPIRE as of 03 Nov 2013

@@

@@

@@

\cite{Sper13}
\bibitem{Sper13} 
  M.~Sperling, D.~Stöckinger and A.~Voigt,
  %``Renormalization of vacuum expectation values in spontaneously broken gauge theories,''
  JHEP {\bf 1307}, 132 (2013)
  [arXiv:1305.1548 [hep-ph]].
  %%CITATION = ARXIV:1305.1548;%%
  %4 citations counted in INSPIRE as of 14 Oct 2013

>>>>

\subsection{Model parameters and RGEs}
Even in the simplest supersymmetric model the RGEs form a very large
set of coupled non-linear differential equations.  In a general
(softly broken) supersymmetric theory the soft-breaking parameters
depend on themselves and the susy parameters.  However, the susy
parameters are independent of the soft-breaking parameters
\cite{Jones:1974pg,Jones:1983vk,West:1984dg,Martin:1993yx,Yamada:1993ga,MV94,Fonseca:2011vn,Sperling:2013eva,Sperling:2013xqa}.
This makes it possible to split the model parameters into the
following two subsets:
%
\begin{enumerate}
\item \emph{susy parameters:} gauge couplings, superpotential
  parameters and VEVs and
\item \emph{soft-breaking parameters} \cite{Girardello:1981wz}: soft
  linear scalar terms, soft bilinear scalar interactions, soft
  trilinear scalar interactions, soft gaugino mass terms and soft
  scalar squared masses.
\end{enumerate}
%
The susy parameters together with their two-loop renormalisation group
equations are stored in the class \code{<model>_susy_parameters}.  The
soft-breaking model parameters together with their two-loop
renormalisation group equations are stored in the class
\code{<model>_soft_parameters}.  The dependence of the soft-breaking
parameters on the susy parameters is implemented via inheritance, see
\figurename~\ref{fig:parameter-classes}, where
\code{<model>_soft_parameters} inherits from
\code{<model>_susy_parameters}.  In this way, the class
\code{<model>_soft_parameters} can implement the soft-breaking beta
functions in terms of the susy and soft-breaking parameters, while the
class \code{<model>_susy_parameters} is independent of the
soft-breaking parameters.
%
\begin{figure}
  \centering
  \tikzumlset{fill class=white}
  \begin{tikzpicture}
    \umlclass[x=0, y=3]{model\_susy\_parameters}{
      - susy parameters
    }{
      + beta()
    }
    \umlclass[x=0, y=0]{model\_soft\_parameters}{
      - soft-breaking parameters
    }{
      + beta()
    }
    \umlinherit{model\_soft\_parameters}{model\_susy\_parameters}
  \end{tikzpicture}
  \caption{Model parameter class structure.}
  \label{fig:parameter-classes}
\end{figure}

@@

\section{Implementing new models}
\section{Adapting the code at the C++ level}
\section{Using individual modules in your own code}

@@

                          & Intel Core2 Duo (P8600)    & Intel Core2 Duo (P8600)     & Intel Xeon (L5640)\\

@@

\begin{thebibliography}{100}
%\cite{Girardello:1981wz}
\bibitem{Girardello:1981wz}
  L.~Girardello and M.~T.~Grisaru,
  %``Soft Breaking of Supersymmetry,''
  Nucl.\ Phys.\ B {\bf 194} (1982) 65.
  %%CITATION = NUPHA,B194,65;%%
  %717 citations counted in INSPIRE as of 21 Feb 2014

%\cite{Allanach:2001kg}
\bibitem{Allanach:2001kg} 
  B.~C.~Allanach,
  %``SOFTSUSY: a program for calculating supersymmetric spectra,''
  Comput.\ Phys.\ Commun.\  {\bf 143}, 305 (2002)
  [hep-ph/0104145].
  %%CITATION = HEP-PH/0104145;%%
  %716 citations counted in INSPIRE as of 20 Sep 2013
%\cite{Porod:2003um}
\bibitem{Porod:2003um} 
  W.~Porod,
  %``SPheno, a program for calculating supersymmetric spectra, SUSY particle decays and SUSY particle production at e+ e- colliders,''
  Comput.\ Phys.\ Commun.\  {\bf 153}, 275 (2003)
  [hep-ph/0301101].
  %%CITATION = HEP-PH/0301101;%%
  %413 citations counted in INSPIRE as of 03 Nov 2013

@@

%\cite{Jones:1974pg}
\bibitem{Jones:1974pg}
  D.~R.~T.~Jones,
  %``Asymptotic Behavior of Supersymmetric Yang-Mills Theories in the Two Loop Approximation,''
  Nucl.\ Phys.\ B {\bf 87} (1975) 127.
  %%CITATION = NUPHA,B87,127;%%
  %123 citations counted in INSPIRE as of 21 Feb 2014

%\cite{Jones:1983vk}
\bibitem{Jones:1983vk}
  D.~R.~T.~Jones and L.~Mezincescu,
  %``The Beta Function in Supersymmetric {Yang-Mills} Theory,''
  Phys.\ Lett.\ B {\bf 136} (1984) 242.
  %%CITATION = PHLTA,B136,242;%%
  %109 citations counted in INSPIRE as of 21 Feb 2014

%\cite{West:1984dg}
\bibitem{West:1984dg}
  P.~C.~West,
  %``The Yukawa beta Function in N=1 Rigid Supersymmetric Theories,''
  Phys.\ Lett.\ B {\bf 137} (1984) 371.
  %%CITATION = PHLTA,B137,371;%%
  %134 citations counted in INSPIRE as of 21 Feb 2014

%\cite{Martin:1993yx}
\bibitem{Martin:1993yx}
  S.~P.~Martin and M.~T.~Vaughn,
  %``Regularization dependence of running couplings in softly broken supersymmetry,''
  Phys.\ Lett.\ B {\bf 318} (1993) 331
  [hep-ph/9308222].
  %%CITATION = HEP-PH/9308222;%%
  %220 citations counted in INSPIRE as of 21 Feb 2014

%\cite{Yamada:1993ga}
\bibitem{Yamada:1993ga}
  Y.~Yamada,
  %``Two loop renormalization of gaugino masses in general supersymmetric gauge models,''
  Phys.\ Rev.\ Lett.\  {\bf 72} (1994) 25
  [hep-ph/9308304].
  %%CITATION = HEP-PH/9308304;%%
  %48 citations counted in INSPIRE as of 21 Feb 2014

@@

%\cite{Fonseca:2011vn}
\bibitem{Fonseca:2011vn}
  R.~M.~Fonseca, M.~Malinsky, W.~Porod and F.~Staub,
  %``Running soft parameters in SUSY models with multiple U(1) gauge factors,''
  Nucl.\ Phys.\ B {\bf 854} (2012) 28
  [arXiv:1107.2670 [hep-ph]].
  %%CITATION = ARXIV:1107.2670;%%
  %29 citations counted in INSPIRE as of 21 Feb 2014

@@

%\cite{Sperling:2013eva}
\bibitem{Sperling:2013eva}
  M.~Sperling, D.~Stöckinger and A.~Voigt,
  %``Renormalization of vacuum expectation values in spontaneously broken gauge theories,''
  JHEP {\bf 1307} (2013) 132
  [arXiv:1305.1548 [hep-ph]].
  %%CITATION = ARXIV:1305.1548;%%
  %10 citations counted in INSPIRE as of 21 Feb 2014

%\cite{Sperling:2013xqa}
\bibitem{Sperling:2013xqa}
  M.~Sperling, D.~Stöckinger and A.~Voigt,
  %``Renormalization of vacuum expectation values in spontaneously broken gauge theories: Two-loop results,''
  JHEP {\bf 1401} (2014) 068
  [arXiv:1310.7629 [hep-ph]].
  %%CITATION = ARXIV:1310.7629;%%
  %4 citations counted in INSPIRE as of 21 Feb 2014
